
---
title: "GP.Corr.11Aug23"
author: "bvt" 
date: "2023-08-30"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GP RSO Time series

**Objective:**

Match, as close as possible, GP sets from different catalogs

**Discussion:**

This is how to download the entire space-track catalog
https://www.space-track.org/basicspacedata/query/class/gp/NORAD_CAT_ID/>1/orderby/CCSDS_OMM_VERS asc/format/csv/emptyresult/show
From Celestrak
https://celestrak.org/satcat/search.php - download the raw csv, rename the 'satcat' to 'celestrak.satcat.day/Month/year

There are many ways to understand a system's behavior using statistical
analysis of the generated output data. 


```{r cars, eval=FALSE, include=FALSE}
summary(cars)
```

```{r initial, message=TRUE, warning=FALSE, include=FALSE}
#library(lubridate)
#library(rgl)
library(ggplot2)
# library(knitr)
# library(fBasics)
library(tidyverse)
# library(RecordLinkage)
# library(cluster)
# library(proxy)
library(asteRisk)

# set your working directory
setwd("/home/bvt/Dropbox/eng_science/R/wd/GP_Corr")

knitr::opts_knit$set(root.dir = "/home/bvt/Dropbox/eng_science/R/wd/GP_Corr")

```

## Correlation Applications

Applications



```{r prepare.data, echo=FALSE, warning=FALSE, results='asis'}
# load in the data sets
df.source.1 <- read.csv("data/st_25544.history.csv", sep = ",", header = TRUE)
# added mean_motion = 1 / (period/1440) value to celestrak
df.source.1$MEAN_MOTION <- ((1) / (df.source.1$PERIOD/1440))
# massage the data by sub-setting the rows and columns into some more mangable and for specific searches,
# Altitude = (Mean Motion)^2 * 6,371,000 * (1 - Eccentricity^2)^-1/2
# The approximate mean motion for a satellite in the 800-850 range is 14.4-15.1 revolutions per day.
# Mean Motion = sqrt(6,371,000 / Altitude)
df.source.1.sel <- 
                df.source.1 %>% 
                #select(OBJECT_ID, OBJECT_NAME, INCLINATION, MEAN_MOTION) %>%
                #select(NORAD_CAT_ID, INCLINATION, MEAN_MOTION) %>%
                #filter(between(MEAN_MOTION, 14.40, 14.402))
                filter(between(CREATION_DATE, "2004-08-17T15:22:27", "2004-08-17T15:22:45"))
                #print()


#cat("==========================================================================================================")

#cat("==========================================================================================================")

```


```{r coor.1, eval=FALSE, message=TRUE, warning=TRUE, include=FALSE}
#df.rowname.1 <- rownames(df.source.1.sel[1])
library(asteRisk)

# Set the Keplerian orbital elements
a <- df.source.1$SEMIMAJOR_AXIS
e <- df.source.1$ECCENTRICITY
i <- df.source.1$INCLINATION #iclination
M <- df.source.1$MEAN_ANOMALY # mean anomoly
omega <- df.source.1$ARG_OF_PERICENTER # omega
OMEGA <- df.source.1$RA_OF_ASC_NODE # OMEGA

# Calculate the ECI coordinates
position_ECI <- KOEtoECI(a, e, i, M, omega, OMEGA)
position_ECI <- KOEtoECI(a, e, i, M, omega, OMEGA)
position_ECI <- KOEtoECI(select(df.source.1, a, e, i, M, omega, OMEGA))
position_ECI <- apply(d)

# Print the ECI coordinates
print(position_ECI)

```

```{r coor.2, eval=FALSE, include=FALSE}
# from Bard
library(asteRisk)

# Create a function to calculate the ECI coordinates
KOEtoECI <- function(a, e, i, M, omega, OMEGA) {
  # Calculate the ECI coordinates
  x <- a * (cos(M) * cos(i) - e * cos(omega) * sin(i))
  y <- a * (sin(M) * cos(i) + e * cos(omega) * cos(i) * sin(M))
  z <- a * (sin(i) * sqrt(1 - e^2)) * sin(M)

  # Return the ECI coordinates
  return(c(x, y, z))
}

# Create a data frame
df <- data.frame(
  a = c(6378137, 6378137),
  e = c(0.009, 0.009),
  i = c(90, 90),
  M = c(0, 0),
  omega = c(0, 0),
  OMEGA = c(0, 0)
)

# Calculate the ECI coordinates for each row
xyz <- apply(df.source.1.sel, 1, KOEtoECI)

# Print the ECI coordinates
print(xyz)

```

```{r coor.3}
# from Bard
library(asteRisk)
#library(satellite)
#library(raster)
library(asteRisk)
results_list <- list()
data <- data.frame(a = c(1, 1.1, 1.05), e = c(0.1, 0.12, 0.2), i = c(0.3, 0.3, 0.301), M = c(0.5, 0.6, 0.5), omega = c(0.7, 0.67, 0.8), OMEGA = c(0.9, 0.93, 0.91))

#for (i in 1:nrow(df.source.1.sel)) {
#result <- with(df.source.1.sel[i, ], KOEtoECI(a = SEMIMAJOR_AXIS, e = ECCENTRICITY, i = INCLINATION, M = MEAN_ANOMALY, omega = PERIAPSIS, OMEGA = RA_OF_ASC_NODE))
  print(result)
#}
for (i in 1:nrow(data)) {
result <- with(data[i, ], KOEtoECI(a, e, i, M, omega, OMEGA))
  results_list[[i]] <- result
}
# Right Ascension of the Ascending Node (Ω)
# Argument of Periapsis (ω)
print(as.data.frame(results_list))
```

placeholder
```{r coor.4, eval=FALSE, include=FALSE}
# # Create an empty list to store the results
results_list <- list()

# Loop through each row in the data frame
for (i in 1:nrow(data)) {
  # Extract Keplerian elements for the current row
  a <- data[i, "a"]
  e <- data[i, "e"]
  i <- data[i, "i"]
  M <- data[i, "M"]
  omega <- data[i, "omega"]
  OMEGA <- data[i, "OMEGA"]
}
  # Use the KOEtoECI function to compute ECI coordinates
result <- KOEtoECI(a, e, i, M, omega, OMEGA)
  
  # Store the result in the list
  results_list[[i]] <- result
}

# Convert the list of coordinates to a data frame
eci_df <- as.data.frame(do.call(rbind, results_list))
colnames(eci_df) <- c("x", "y", "z")

# Print the resulting ECI coordinates
print(eci_df)

```

```{r match, eval=FALSE, include=FALSE}

# Sample data in two data frames with row names
df_company1 <- data.frame(
  RSO_ID = c("ST1", "ST2", "ST3"),
  X = c(1.0, 1.1, 3.0),  # 
  Y = c(0.5, 1.5, 2.5),   # 
  Z = c(0.94, 1.6, 2.3)   # 
)
df_company2 <- data.frame(
  RSO_ID = c("CT1", "CT2", "CT3"),
  X = c(1.02, 2.3, 3.0),  # 
  Y = c(0.5, 1.5, 2.44),   # 
  Z = c(0.35, 1.2, 2.3)   # 
)

# Extract the Keplerian elements from each data.frame
df1_keplerian <- df_company1[, c("X", "Y", "Z")]
df2_keplerian <- df_company2[, c("X", "Y", "Z")]

# Calculate the Euclidean distance matrix using the dist function
euclidean_matrix <- as.matrix(dist(rbind(df1_keplerian, df2_keplerian)))

# Label the rows and columns of the matrix with the RSO_IDs
rownames(euclidean_matrix) <- c(df_company1$RSO_ID, df_company2$RSO_ID)
colnames(euclidean_matrix) <- rownames(euclidean_matrix)

# Print out the labeled results
print(euclidean_matrix)
#print(euclidean_matrix[lower.tri(euclidean_matrix, diag = TRUE)])
# Your existing code to calculate the Euclidean distance matrix...
# (Same as the code you provided)

# Get the lower triangular elements and set upper triangular elements to NA
lower_tri_matrix <- euclidean_matrix
lower_tri_matrix[upper.tri(lower_tri_matrix)] <- NA

# Print out the labeled lower triangular part of the matrix without showing 'NA' values
print(lower_tri_matrix)
```

```{r GPT.4, eval=FALSE, include=FALSE}

library(asteRisk)

# Create a function to calculate the ECI coordinates
KOEtoECI <- function(a, e, i, M, omega, OMEGA) {
  # Calculate the ECI coordinates
  x <- a * (cos(M) * cos(i) - e * cos(omega) * sin(i))
  y <- a * (sin(M) * cos(i) + e * cos(omega) * cos(i) * sin(M))
  z <- a * (sin(i) * sqrt(1 - e^2)) * sin(M)

  # Return the ECI coordinates
  return(c(x, y, z))
}

# Create a data frame
df <- data.frame(
  a = c(6378137, 6378137),
  e = c(0.009, 0.009),
  i = c(90, 90),
  M = c(0, 0),
  omega = c(0, 0),
  OMEGA = c(0, 0)
)

# Calculate the ECI coordinates for each row
#xyz <- apply(df, 1, KOEtoECI)

# Print the ECI coordinates
#print(xyz)

```


```{r PDF.1, eval=FALSE, include=FALSE}



```


```{r Notes, eval=FALSE, include=FALSE}
# Work Notes
# Entity Resoultion - https://github.com/cleanzr/record-linkage-tutorial
# https://cran.r-project.org/web/packages/diyar/vignettes/links.html
# https://stats.stackexchange.com/questions/15289/when-to-use-weighted-euclidean-distance-and-how-to-determine-the-weights-to-use#15325
# https://en.wikipedia.org/wiki/Mahalanobis_distance
# https://www.youtube.com/watch?v=hyNPsstKhfQ&t=677s
# EM - https://www.codingninjas.com/blog/2020/09/15/what-is-em-algorithm-in-machine-learning/
# https://medium.com/@gshriya195/top-5-distance-similarity-measures-implementation-in-machine-learning-1f68b9ecb0a3
# euclidean <- function(a,b) sqrt(sum((a-b^2)))
# nice list of distance types - https://www.statology.org/dist-function-in-r/
# https://rdrr.io/cran/asteRisk/f/vignettes/asteRisk.Rmd
#https://www.space-track.org/basicspacedata/query/class/gp_history/OBJECT_ID/25544/orderby/CCSDS_OMM_VERS asc/emptyresult/show
```
